\section{Introduction}

Cryptographic algorithms and protocols are quickly becoming more prevelant,
more special purpose, and more complex. In the face of this reasoning about their
correctness is still not easy, and requires a combination of proof, testing,
and peer review. Many of these algorithms have also become essential to
operation of services we rely on in our day to day lives, and we
require their implementations to not only be correct, but fast to scale to
real world use.

The question becomes: How do give cryptographers powerful tools to specify, verify,
test and optimize algorithms? Traditionally each acitivity has required a different
sets of tools that worked in isolation. Our goal in this paper is to introduce
a framework that allows us to perform each activity with a single tool chain.

We allow the user of our tool to write down executable specifications of
their algorithms with boths proofs and examples as well as exposing machinery for
automatically solving common proof obligations.

We can leverage the power of this approach in order to build our
specification language. By embedding our language into the theorem prover Lean
we gain all of its theorem proving power and capbilities. Lean is a good choice here because
its foundational system is type theory, enabling us directly execute programs
written in the framework. This is a well known technique for verifying
computational domains, it is discussed in depth in section \ref{relatedwork}.

We implement a embedded domain specific language inside of Lean built around
the manipulation of depedently typed bit vectors, allowing us to verify
the correctness of algorithms and extract an implementation.
